You have more money in your wallet. This does not mean you will spend extra on food

### 2024-04-17 paper/paper.qmd
added interactive plot
updated the qmd file with interactive map.

We create this project using statistical software, `R` [@citeR]. For cleaning and re-purposing the data, we used `tidyverse` [@tidy] package and graphs, we relied on `ggplot2` [@ggplot2]. The data used in this paper comes from `fredr` [@fredr] package. We further used `rstanarm` [@rstanarm] and `modelsummary` [@ms] for modelling. Lastly, we used `kableExtra` [@kable] and `viridis` [@viridis] for aesthetics purposes. For editing texts, we used `rspell` library [@rspell].

@@

formatted_data[1:12,] |> 
  kable(col.names = c("Date", "Durable goods", "Non-durable goods", "Food", "Disposable income",
                      "Healthcare", "Services"),
        booktabs = TRUE,
        linesep = "",
        align = "c",
        format = "latex") |> 
  column_spec(c(1, 2, 3, 4, 5, 6, 7), width = "6em") |> 
  kable_styling(font_size = 9, latex_options = "scale_down")  |>
  add_footnote(c("Note: The table displays data from 2007-2009 to illustrate the aggregated clean data. Including the entire dataset would be redundant and unnecessarily clutter the display."))
```

@@

All datasets underwent seasonal adjustment and were indexed to 2017 dollars. Seasonal adjustments mitigate the influence of periodic fluctuations, such as strikes or unusual weather events, which can obscure genuine economic trends. By referencing all data to the 2017 price level, we adjusted for inflation over time, facilitating accurate comparisons across various periods. Additionally, utilizing real economic data rather than nominal figures allowed for valid comparisons between different categories across time frames

@@

Furthermore, the "value" column records expenditures in billions of US dollars. For a comparative analysis of each category, please refer to @fig-2. The cleaned data utilized for modeling and analysis is detailed in @tbl-2. The datasheet is accessible in @sec-appen for further reference.

@@

We use ran trace plots for both models and we are interested in understanding whether the algorithm ran into any issues [@Alexander_2023]. Looking at the plots for both models, we do not encounter any out of the ordinary events.

>>>>

We create this project using statistical software, `R` [@citeR]. For cleaning and re-purposing the data, we used `tidyverse` [@tidy] package and graphs, we relied on `ggplot2` [@ggplot2]. The data used in this paper comes from `fredr` [@fredr] package. We further used `rstanarm` [@rstanarm] and `modelsummary` [@ms] for modelling. Lastly, we used `kableExtra` [@kable] and `viridis` [@viridis] for aesthetics purposes. For editing texts, we used `rspell` library [@rspell]. We created interactive map using `plotly` [@plotly] library and published through `shiny` library [@shiny].

@@

formatted_data[1:12,] |> 
  kable(col.names = c("Date", "Durable goods", "Non-durable goods", "Food", "Disposable income",
                      "Healthcare", "Services"),
        booktabs = TRUE,
        linesep = "",
        align = "c",
        format = "latex") |> 
  column_spec(c(1, 2, 3, 4, 5, 6, 7), width = "6em") |> 
  kable_styling(font_size = 9, latex_options = "scale_down")  |>
  add_footnote(c("Note: The table displays data from 2007-2009 to illustrate the aggregated clean data. Including the entire dataset would be redundant and unnecessarily clutter the display. To get a better understanding of how the data looks like in entirety, please check out the interactive graph. The link can be found on the Github page"))
```

@@

All datasets underwent seasonal adjustment and were indexed to 2017 dollars. Seasonal adjustments mitigate the influence of periodic fluctuations, such as strikes or unusual weather events, which can obscure genuine economic trends. By referencing all data to the 2017 price level, we adjusted for inflation over time, facilitating accurate comparisons across various periods. Additionally, utilizing real economic data rather than nominal figures allowed for valid comparisons between different categories across time frames.

@@

Furthermore, the "value" column records expenditures in billions of US dollars. For a comparative analysis of each category, please refer to @fig-2. The cleaned data utilized for modeling and analysis is detailed in @tbl-2. The datasheet is accessible in @sec-appen for further reference. You can find an interactive plot showing the evolution of each expenditure variable on our GitHub page.

@@

We ran trace plots for both models as we were interested in understanding whether the algorithm ran into any issues [@Alexander_2023]. Looking at the plots for both models, we do not encounter any out of the ordinary events.
